Dependent Object Types

### 2012-09-07 doc/candidacy/slides.tex
formatting
system F_omega backup slide

\inputminted[frame=lines,fontsize=\footnotesize]{scala}{intro.scala}
\end{frame}

@@

\begin{frame}{ML-Like: Calculus}
grounded in type theory; based on Girard's $F_\omega$, adding: % quick summary of F_\omega
\begin{itemize}
\item {\it translucent sums} to model modules
\item dependent functions to model functors
\item a notion of subtyping to model module implementation-interface matching
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Tribe Types}
\begin{itemize}
\item in Tribe, types are a form of generalized paths: a final
  variable, {\tt this} or a class name then followed by a possibly
  empty sequence of field, {\tt out} or class selections
\item {\tt kitt.Passenger.name}: the name of one of Kitt's passengers
\item {\tt kitt.driver <: Car.driver <: Car.Passenger <: Car.Traveller <:
  Vehicle.Traveller}
\item {\tt kitt.driver $\not<:$ karr.driver} and {\tt kitt.Passenger $\not<:$ karr.Passenger}
\end{itemize}
\begin{minted}[frame=lines,fontsize=\footnotesize]{java}
class Vehicle { class Traveller { ... } }
class Car extends Vehicle {
  class Passenger extends Traveller {
    class String { ... }
    final String name;
  }
  final Passenger driver;
}
final Car kitt;
final Car karr;
\end{minted}
\end{frame}

@@

% System F omega
% System F sub
\end{document}

>>>>

\inputminted[fontsize=\footnotesize]{scala}{intro.scala}
\end{frame}

@@

\begin{frame}{ML-Like: Calculus}
grounded in type theory; based on Girard's $F_\omega$, adding:
\begin{itemize}
\item {\it translucent sums} to model modules
\item dependent functions to model functors
\item a notion of subtyping to model module implementation-interface matching
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Tribe Types}
\begin{itemize}
\item in Tribe, types are a form of generalized paths: a final
  variable, {\tt this} or a class name then followed by a possibly
  empty sequence of field, {\tt out} or class selections
\item {\tt kitt.Passenger.name}: the name of one of Kitt's passengers
\item {\tt kitt.driver <: Car.driver <: Car.Passenger <: Car.Traveller <:
  Vehicle.Traveller}
\item {\tt kitt.driver $\not<:$ karr.driver} and {\tt kitt.Passenger $\not<:$ karr.Passenger}
\end{itemize}
\begin{minted}[fontsize=\footnotesize]{java}
class Vehicle { class Traveller { ... } }
class Car extends Vehicle {
  class Passenger extends Traveller {
    class String { ... }
    final String name;
  }
  final Passenger driver;
}
final Car kitt;
final Car karr;
\end{minted}
\end{frame}

@@

\begin{frame}[fragile]{System $F_\omega$: Higher-order polymorphic lambda-calculus}
\begin{description}[1234567890]
\item[terms $t$]
\begin{description}[123456789012345678901234567890]
\item[typed lambda-calculus terms] $x$ -- $\lambda x:T.t$ -- $t t$
\item[type abstraction] $\lambda X::K.t$
\item[type application] $t [T]$
\end{description}
\item[types $T$]
\begin{description}[123456789012345678901234567890]
\item[type variable] $X$
\item[type of functions] $T \rightarrow T$
\item[universal type] $\forall X::K.T$
\item[operator abstraction] $\lambda X::K.T$
\item[operator application] $T T$
\end{description}
\item[kinds $K$]
\begin{description}[123456789012345678901234567890]
\item[kind of proper types] $*$
\item[kind of operators] $K \Rightarrow K$
\end{description}
\end{description}
\end{frame}

% System F sub
\end{document}
